#Running DeSeq2 for diff gene exp

#Load libraries
```{r}
library(scater)
library(Seurat)
library(cowplot)
library(Matrix.utils)
library(edgeR)
library(dplyr)
library(magrittr)
library(Matrix)
library(purrr)
library(reshape2)
library(S4Vectors)
library(tibble)
library(SingleCellExperiment)
library(pheatmap)
library(apeglm)
library(png)
library(DESeq2)
library(RColorBrewer)
library(Seurat)
library(dplyr)
library(tibble)
library(stringr)
library(circlize)
library(readr)
library(enrichR)
library(lme4)
library(lmerTest)
library(philentropy)
library(ggplot2)
library(circlize)
library(ComplexHeatmap)
library(dendextend)
```


```{r}
#Import gene-filtered cell-type seurat object add meta
seurat <- readRDS("/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/CA1_nofilter.rds")

#Add meta and subset for exposure vs condition/time
seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC1')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC1')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC1')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC1')]<-"32"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC1')]<-"A"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC1')]<-"Con1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC1')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC1')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC1')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC1')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC1')]<-"31"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC1')]<-"A"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC1')]<-"Ucon1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC1')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC2')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC2')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC2')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC2')]<-"33"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC2')]<-"B"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC2')]<-"Con0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC2')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC2')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC2')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC2')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC2')]<-"34"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC2')]<-"B"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC2')]<-"Ucon0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC2')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('NC2')]<-"Naive"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('NC2')]<-"Base"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('NC2')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('NC2')]<-"30"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('NC2')]<-"A"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('NC2')]<-"Naive"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC3')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC3')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC3')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC3')]<-"30"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC3')]<-"C"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC3')]<-"Con1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC3')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC3')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC3')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC3')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC3')]<-"31"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC3')]<-"C"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC3')]<-"Ucon1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC3')]<-"Exposed"

seurat@meta.data$time[seurat@meta.data$orig.ident==c('NC3')]<-"Base"
seurat@meta.data$condition[seurat@meta.data$orig.ident==c('NC3')]<-"Naive"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('NC3')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('NC3')]<-"32"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('NC3')]<-"C"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('NC3')]<-"Naive"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC4')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC4')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC4')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC4')]<-"44"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC4')]<-"D"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC4')]<-"Con0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC4')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC4')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC4')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC4')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC4')]<-"43"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC4')]<-"D"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC4')]<-"Ucon0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC4')]<-"Exposed"

seurat@meta.data$time[seurat@meta.data$orig.ident==c('NC4')]<-"Base"
seurat@meta.data$condition[seurat@meta.data$orig.ident==c('NC4')]<-"Naive"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('NC4')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('NC4')]<-"33"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('NC4')]<-"E"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('NC4')]<-"Naive"


seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC5')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC5')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC5')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC5')]<-"45"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC5')]<-"D"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC5')]<-"Con1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC5')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC5')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC5')]<-"1hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC5')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC5')]<-"32"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC5')]<-"E"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC5')]<-"Ucon1"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC5')]<-"Exposed"

seurat@meta.data$time[seurat@meta.data$orig.ident==c('NC5')]<-"Base"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('NC5')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('NC5')]<-"31"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('NC5')]<-"F"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('NC5')]<-"Naive"
seurat@meta.data$condition[seurat@meta.data$orig.ident==c('NC5')]<-"Naive"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('FC6')]<-"Conditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('FC6')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('FC6')]<-"Male"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('FC6')]<-"30"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('FC6')]<-"F"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('FC6')]<-"Con0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('FC6')]<-"Exposed"

seurat@meta.data$condition[seurat@meta.data$orig.ident==c('UC6')]<-"Unconditioned"
seurat@meta.data$time[seurat@meta.data$orig.ident==c('UC6')]<-"0hr"
seurat@meta.data$sex[seurat@meta.data$orig.ident==c('UC6')]<-"Female"
seurat@meta.data$age[seurat@meta.data$orig.ident==c('UC6')]<-"32"
seurat@meta.data$batch[seurat@meta.data$orig.ident==c('UC6')]<-"F"
seurat@meta.data$condition_time[seurat@meta.data$orig.ident==c('UC6')]<-"Ucon0"
seurat@meta.data$exposure[seurat@meta.data$orig.ident==c('UC6')]<-"Exposed"
```

#Make se and run deseq for exposure-induced changes in gene expression
```{r}
gene_se <- SummarizedExperiment(as.matrix(seurat@assays$RNA@counts),colData = seurat@meta.data)

gene_dds <- DESeqDataSet(gene_se, design = ~ batch + exposure)

gene_dds <- DESeq(gene_dds,fitType = "local",useT=TRUE,minmu=1e-6,minReplicatesForReplace=Inf,test="LRT",reduced=~batch)

saveRDS(gene_dds, file='/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq_genes_exposure.rds')
gene_res_LRT <- results(gene_dds)
gene_sig_res_LRT <- gene_res_LRT %>%
              data.frame() %>%
              rownames_to_column(var="gene") %>% 
              as_tibble() %>% 
              filter(padj < .1)
saveRDS(gene_sig_res_LRT, '/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq2_genes_exposure.rds')
```


#ok what do the results look like if we try to model them without DeSeq2 fitting
```{r}
#Just scale to avg UMIs/cell, don't norm (stored in data slot)
scalef <- mean(seurat@meta.data[["nCount_RNA"]])
exposure <- NormalizeData(seurat, normalization.method = "RC", scale.factor=scalef)
```

```{r}
exp_genes <- vector()
p_vals <- vector()
estimates <- vector()
#for (gene in rownames(seurat)){
#Set up obs x variables matrix (cells x meta)
horses <- as.data.frame(seurat@meta.data)
horses$cell <- rownames(horses)

counts <- GetAssayData(object = seurat, slot = "counts")
subset <- as.matrix(counts['Ywhaz',])



horses$counts <- as.vector(subset[,1])

#horses$scaled <- scale(horses$nCount_RNA)


model <- glmer.nb(counts ~ exposure +(1|batch), data=horses)

#This is pretty consistent with Deseq2 but Deseq2 does put more care into gene-wise disp 
#estimates so let's move forwward with deseq2 for experience-induced genes 
```


#Subset to UC and FC
```{r}
seurat <- subset(seurat, subset = exposure == 'Naive', invert=TRUE)

#Run deseq for condition-induced changes in gene expression
gene_se <- SummarizedExperiment(as.matrix(seurat@assays$RNA@counts),colData = seurat@meta.data)

gene_dds <- DESeqDataSet(gene_se, design = ~ batch+sex+condition)

gene_dds <- DESeq(gene_dds,fitType = "local",useT=TRUE,minmu=1e-6,minReplicatesForReplace=Inf,test="LRT",reduced=~batch+sex)

saveRDS(gene_dds, file='/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq_genes_condition.rds')

#Run deseq for time-induced changes in gene expression
gene_dds <- DESeqDataSet(gene_se, design = ~ batch+sex+time)

gene_dds <- DESeq(gene_dds,fitType = "local",useT=TRUE,minmu=1e-6,minReplicatesForReplace=Inf,test="LRT",reduced=~batch+sex)

saveRDS(gene_dds, file='/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq_genes_time.rds')
```

#####for raw isoform exp
#Import count/tx/cell matrix and add meta
```{r}
#Import per-cell isoform counts from raw salmon
seurat_dir="/Seurat_Input"
home_dir<-"/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/novelisoforms/finalfastas/"
samples <-list("FC1","UC1","FC2","UC2","NC2","FC3","UC3","NC3","FC4","UC4","NC4","FC5","UC5","NC5","FC6","UC6")
for (item in samples){
  data_dir <- paste(home_dir, item, seurat_dir, sep = "")
  expressionmatrix <-Read10X(data.dir = data_dir)
  assign(item, CreateSeuratObject(counts = expressionmatrix, project = item))}

#Merge sample datasets into one large Seurat object
samples <-list("FC1","UC1","FC2","UC2","NC2","FC3","UC3","NC3","FC4","UC4","NC4","FC5","UC5","NC5","FC6","UC6")
isoform.combined <- merge(FC1, y = c(UC1,FC2,UC2,NC2,FC3,UC3,NC3,FC4,UC4,NC4,FC5,UC5,NC5,FC6,UC6), add.cell.ids = samples, project = "isoformcombined")

#Add meta and subset for exposure vs condition/time
isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC1')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC1')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC1')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC1')]<-"32"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC1')]<-"A"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC1')]<-"Con1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC1')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC1')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC1')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC1')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC1')]<-"31"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC1')]<-"A"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC1')]<-"Ucon1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC1')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC2')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC2')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC2')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC2')]<-"33"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC2')]<-"B"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC2')]<-"Con0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC2')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC2')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC2')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC2')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC2')]<-"34"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC2')]<-"B"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC2')]<-"Ucon0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC2')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('NC2')]<-"Naive"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('NC2')]<-"Base"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('NC2')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('NC2')]<-"30"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('NC2')]<-"A"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('NC2')]<-"Naive"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC3')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC3')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC3')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC3')]<-"30"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC3')]<-"C"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC3')]<-"Con1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC3')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC3')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC3')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC3')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC3')]<-"31"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC3')]<-"C"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC3')]<-"Ucon1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC3')]<-"Exposed"

isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('NC3')]<-"Base"
isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('NC3')]<-"Naive"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('NC3')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('NC3')]<-"32"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('NC3')]<-"C"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('NC3')]<-"Naive"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC4')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC4')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC4')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC4')]<-"44"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC4')]<-"D"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC4')]<-"Con0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC4')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC4')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC4')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC4')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC4')]<-"43"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC4')]<-"D"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC4')]<-"Ucon0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC4')]<-"Exposed"

isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('NC4')]<-"Base"
isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('NC4')]<-"Naive"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('NC4')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('NC4')]<-"33"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('NC4')]<-"E"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('NC4')]<-"Naive"


isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC5')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC5')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC5')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC5')]<-"45"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC5')]<-"D"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC5')]<-"Con1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC5')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC5')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC5')]<-"1hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC5')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC5')]<-"32"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC5')]<-"E"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC5')]<-"Ucon1"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC5')]<-"Exposed"

isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('NC5')]<-"Base"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('NC5')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('NC5')]<-"31"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('NC5')]<-"F"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('NC5')]<-"Naive"
isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('NC5')]<-"Naive"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('FC6')]<-"Conditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('FC6')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('FC6')]<-"Male"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('FC6')]<-"30"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('FC6')]<-"F"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('FC6')]<-"Con0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('FC6')]<-"Exposed"

isoform.combined@meta.data$condition[isoform.combined@meta.data$orig.ident==c('UC6')]<-"Unconditioned"
isoform.combined@meta.data$time[isoform.combined@meta.data$orig.ident==c('UC6')]<-"0hr"
isoform.combined@meta.data$sex[isoform.combined@meta.data$orig.ident==c('UC6')]<-"Female"
isoform.combined@meta.data$age[isoform.combined@meta.data$orig.ident==c('UC6')]<-"32"
isoform.combined@meta.data$batch[isoform.combined@meta.data$orig.ident==c('UC6')]<-"F"
isoform.combined@meta.data$condition_time[isoform.combined@meta.data$orig.ident==c('UC6')]<-"Ucon0"
isoform.combined@meta.data$exposure[isoform.combined@meta.data$orig.ident==c('UC6')]<-"Exposed"

exposure <- isoform.combined
condition_time <- subset(isoform.combined, subset = exposure == 'Naive', invert=TRUE)
```

#Make se and run deseq for exposure-induced changes in isoform expression
```{r}
tx_se <- SummarizedExperiment(as.matrix(exposure@assays$RNA@counts),colData = exposure@meta.data)

#pseduo +1 to first row just to get deseq2 to be quiet
for (cell in colnames(exposure)){
  tx_se@assays@data@listData[[1]][1,cell] <- (tx_se@assays@data@listData[[1]][1,cell])+1
}

tx_dds <- DESeqDataSet(tx_se, design = ~ batch+sex+exposure)

tx_dds <- DESeq(tx_dds,fitType = "local",useT=TRUE,minmu=1e-6,minReplicatesForReplace=Inf,test="LRT",reduced=~batch+sex)

saveRDS(tx_dds, file='/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq_tx_exposure.rds')
tx_res_LRT <- results(tx_dds)
tx_sig_res_LRT <- tx_res_LRT %>%
              data.frame() %>%
              rownames_to_column(var="gene") %>% 
              as_tibble() %>% 
              filter(padj < .1)
```

#Make se and run deseq for condition-induced changes in isoform expression
```{r}
tx_se <- SummarizedExperiment(as.matrix(condition_time@assays$RNA@counts),colData = condition_time@meta.data)

#pseduo +1 to first row just to get deseq2 to be quiet
for (cell in colnames(condition_time)){
  tx_se@assays@data@listData[[1]][1,cell] <- (tx_se@assays@data@listData[[1]][1,cell])+1
}

tx_dds <- DESeqDataSet(tx_se, design = ~ batch+sex+condition)

tx_dds <- DESeq(tx_dds,fitType = "local",useT=TRUE,minmu=1e-6,minReplicatesForReplace=Inf,test="LRT",reduced=~batch+sex)

saveRDS(tx_dds, file='/atium/Data/projects/sheridansinglecell/R2C2/Data/CA1/Deseq_tx_condition.rds')
tx_res_LRT <- results(tx_dds)
tx_sig_res_LRT <- tx_res_LRT %>%
              data.frame() %>%
              rownames_to_column(var="gene") %>% 
              as_tibble() %>% 
              filter(padj < .1)
```